---
title: "Assignment: R Markdown Presentation & Plotly"
author: "Author: Poo, L. S."
date: "Date: `r format(Sys.Date(), '%d %B %Y')`"
output: 
  ioslides_presentation: 
    keep_md: TRUE
---

## Loading the Plotly Package

The `plotly` package is loaded for creating interactive plots. The `quantmod` package is loaded. The `quantmod` package (Quantitative Financial Modelling and Trading Framework for R) is designed to assist the quantitative trader in the development, testing, and deployment of statistically based trading models.

```{r message=FALSE}
library(plotly)
library(quantmod)
```

## Reading the Data

The data is sourced using the `quantmod` package. The data contains the stock prices of several NASDAQ-listed companies from the year 2010 to 2016.

```{r message=FALSE, results="hide"}
fdate <- as.Date("01/01/10",
                 format = "%d/%m/%y")
tdate <- as.Date("31/12/16",
                 format = "%d/%m/%y")

getSymbols(c("AAPL", "MSFT", "FB"),
           src = "google",
           from = fdate,
           to = tdate)
```

## Processing the Data

The dates, symbols, and prices are extracted and grouped in a single data frame.

```{r}
mydate <- c(index(AAPL), index(MSFT), index(FB))

AAPL <- data.frame(mysymbol = "Apple Inc. (AAPL)",
                   myprice = as.numeric(AAPL[,1]))
MSFT <- data.frame(mysymbol = "Microsoft Corporation (MSFT)",
                   myprice = as.numeric(MSFT[,1]))
FB <- data.frame(mysymbol = "Facebook, Inc. (FB)",
                 myprice = as.numeric(FB[,1]))

stocks <- rbind(AAPL, MSFT, FB)
stocks <- cbind(mydate, stocks)
```

## Creating an Interactive Plot with Plotly

Here is the code to create an interactive plot using `plot_ly()`.

```{r eval=FALSE}
plot_ly(x = stocks$mydate,
        y = stocks$myprice,
        color = stocks$mysymbol,
        type = "scatter",
        mode = "lines") %>%
    layout(title = "Stock Prices from Year 2010 to 2016",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Stock Price (in USD)"))
```

## Creating an Interactive Plot with Plotly

```{r echo=FALSE, warning=FALSE, fig.width=8}
plot_ly(x = stocks$mydate,
        y = stocks$myprice,
        color = stocks$mysymbol,
        type = "scatter",
        mode = "lines") %>%
    layout(title = "Stock Prices from Year 2010 to 2016",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Stock Price (in USD)"))
```
